\thetitle

### 2021-01-13 paper/paper.tex
ANN setup

\paragraph*{Neural Network Setup.}
%
\MS[t]{TODO}
We use the same setup for the neural network as done by \cite{Schneckenreither2019}. However as they
use a actor-critic agent, whereas we approximate state-action-values the output of the network is a
one dimensional vector as opposed to a matrix. Therefore we use a single three layer fully-connected
network where the number of nodes and activation functions are 41-ReLU\footnote{ReLU stands for
  rectified linear unit.}-89-ReLU-20-ReLU-9, with the output activations being Tanh (hyperbolic
tangent function).
        %
The output for both networks consist of $3^{2}=9$ nodes. This is due to the fact that all
combinations of increase, decrease and no change of the lead time for each product type have to be
represented.
        %
For back-propagation we use the Adam optimiser with learning rate \(0.001\), and beta-values
\(\beta_{1}=0.9\), and \(\beta_{2}=0.999\).

@@

\begin{table}[tb]
  \begin{center}
    \begin{tabular}{c|rrr|c|c||c|c|c|c|c}
      \hline
      80-\(\Exp\)-\(\Unif\)   & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTT+FGIT & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
      \hline
       \rl{0.995}             & 55.218 & 137.006 & 52.090   &          & 244.315 & 1.506 & 2.597    & 0.915  & 34.902   & 32.791             \\
      \rl{1.000}              & 67.265 & 102.180 & 175.686  &          & 345.132 & 1.517 & 2.627    & 0.908  & 49.305   & 30.777             \\
      \BILOne{}               & 45.902 & 0.000   & 734.431  &          & 780.333 & 1.319 & 1.806    & 0.352  &          &                    \\
      \BILTwo{}               & 45.734 & 80.313  & 1425.221 &          & 268.569 & 1.318 & 2.158    & 0.876  &          &                    \\
      \BILThree{}             & 45.861 & 279.723 & 30.818   &          & 356.402 & 1.318 & 3.034    & 0.975  &          &                    \\
      \hline
%
%       \hline
%       80-\(\Unif\)-\(\Exp\) & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\)  & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
    \end{tabular}
  \end{center}
  \caption{\label{tbl:80} Results for a bottleneck utilisation of 80\%. }
\end{table}

>>>>

\paragraph*{Neural Network Setup.}
%
Due to the vast possibilities the neural network architecture was manually optimised, starting with
less stochastic systems and aiming for a coffin shape that can be used in all setups. During this
process we constantly adapted and reevaluated the best network on various production system
configurations. The resulting architecture depends on the number of features \(\anninp\) and the
number of output nodes \(\annout\), which itself depends on the number of actions
\(\acts = \size{\States}\), the independent agent configuration, and the number of functions that
are approximated. For the later, in case of the proposed algorithm this is \(2\),
\(\X^\pol_{\gamma_{0}}\) and \(\X^\pol_{\gamma_{1}}\), while deep Q-Learning only approximates the
function \(Q_{\gamma}^\pol\).
%
The resulting feedforward deep ANN archtiecture is given as %
\(\anninp %
\rightarrow 3 \anninp % \rightarrow \relu
\rightarrow \anninp % \rightarrow \relu
\rightarrow 2 \annout % \rightarrow \relu
\rightarrow \annout %
% \rightarrow   \leakyTanh%
\), where each arrow symbolises a fully-connected layer with a rectified linear unit (\(\relu\)) as
activation function. As output activation function we use the hyperbolic tangent function
(\(\Tanh\)), but similar to leaky \(\relu\), leak values greater than \(0.98\) (less than \(-0.98\))
with \(5\%\). The idea is that we do not want to restrict the approximations to values inside this
range, but values outside of it are less important and thus can be less precise.

The values \(\anninp\) and \(\annout\) depend on the feature extraction method. In case of an
aggregation to product groups \(g\) we have \(\anninp=180\), and due to \(6\) possible actions for
the two independent agents, \(\annout=12\).
% SpecFullyConnected 180 540 :=> SpecRelu (540,1,1) :=> SpecFullyConnected 540 180 :=> SpecRelu
% (180,1,1) :=> SpecFullyConnected 180 24 :=> SpecRelu (24,1,1) :=> SpecFullyConnected 24 12 :=>
% SpecReshape (12,1,1) (6,2,1) :=> SpecLeakyTanh 0.98 (6,2,1) :=> SpecNNil2D 6x2
In the case of the full representation using 6 independent agents the setup is \(\anninp=540\) and
\(\annout=36\).
% SpecFullyConnected 540 1620 :=> SpecRelu (1620,1,1) :=> SpecFullyConnected 1620 540 :=> SpecRelu
% (540,1,1) :=> SpecFullyConnected 540 72 :=> SpecRelu (72,1,1) :=> SpecFullyConnected 72 36 :=>
% SpecReshape (36,1,1) (18,2,1) :=> SpecLeakyTanh 0.98 (18,2,1) :=> SpecNNil2D 18x2
For the Q-Learning algorithm, which only approximates one function, the output nodes
\(\annout\) are halved for both setups.

The ANN is trained using the Adam optimiser \citep{kingma2014adam} with learning rate \(0.0001\),
and the default beta-values \(\beta_{1}=0.9\), and \(\beta_{2}=0.999\). As neural network
initialisation method we use the commonly known Xavier initialisation
\citep{glorot2010understanding}, i.e.\@ the initial value for each weight \(i\) is sampled from a
uniform distribution \(W_{l,i} \sim \Unif(-1/\sqrt{n_l},1/\sqrt{n_l})\), where \(n_{l}\) is the
number of nodes in layer \(l\).

@@

\begin{table}[tb]
  \begin{center}
    \begin{tabular}{c|rrr|c|c||c|c|c|c|c}
      \hline
      80-\(\Exp\)-\(\Unif\)   & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTT+FGIT & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
      \hline
      \rl{0.995}              & 55.22 & 137.00 & 52.09   &          & 244.32 & 1.51 & 2.60    & 0.915  & 34.902   & 32.791             \\
      \rl{1.000}              & 67.27 & 102.18 & 175.69  &          & 345.13 & 1.52 & 2.63    & 0.908  & 49.305   & 30.777             \\
      \BILOne{}               & 45.90 & 0.00   & 734.43  &          & 780.33 & 1.32 & 1.81    & 0.352  &          &                    \\
      \BILTwo{}               & 45.73 & 80.31  & 1425.22 &          & 268.57 & 1.32 & 2.158    & 0.876  &          &                    \\
      \BILThree{}             & 45.86 & 279.72 & 30.82   &          & 356.40 & 1.32 & 3.034    & 0.975  &          &                    \\
      \hline
%
%       \hline
%       80-\(\Unif\)-\(\Exp\) & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
%       \hline
% %
%       \hline
%       80-\(\Exp\)-\(\Exp\)  & WIPC   & FGIC    & BOC      & FGIC+BOC & SUM     & SFTT  & SFTP+FGI & SL(\%) & Cost.p.P & \(\avgrew^{\pol}\) \\
%       \hline                &
%        ANN{}                &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTA{}             &        &         &          &          &         &       &          &        &          &                    \\
%        ESSLTB{}             &        &         &          &          &         &       &          &        &          &                    \\
%        BILD{}               &        &         &          &          &         &       &          &        &          &                    \\
    \end{tabular}
  \end{center}
  \caption{\label{tbl:80} Results for a bottleneck utilisation of 80\%. }
\end{table}
